Test of Adaptable User Interfaces

### 2015-07-09 paper.tex
Adding support for Windows-compiling when eps images included
Adding borders to results tables in Approch section

% =============================================================================
\section{Case Study}
% =============================================================================

\marginpar{
\begin{figure}
  \begin{center}
  \includegraphics[width=\marginparwidth]{images/web0_goal-filter.eps}
  \caption{Une figure dans la marge.}
  \label{fig:marginparsample}
  \end{center}  
\end{figure}

\begin{figure}
  \begin{center}
  \includegraphics[width=\marginparwidth]{images/mobile_goal-filter.eps}
  \caption{Une figure dans la marge.}
  \label{fig:marginparsample}
  \end{center}  
\end{figure}
}

The case study used in this work is a prototype for a smart home energy management system. This decision is based on the fact that it is a modern concept, little explored in the domain of this research and whose UIs can be adapted to several contexts. A smart home may be defined as a well-designed structure with sufficient access to assets, communication, controls, data, and information technologies for enhancing the occupants' quality of life through comfort, convenience, reduced costs and increased connectivity~\cite{smart-home-harper}. A smart home energy management system is an energy management system applied to smart homes. It allows users to control and monitor the energy consumption in a residence from different devices.

It is a prototype because we have developed only the UIs of the system for four versions, three for web environment and one as a mobile application. The data of the system are predetermined. All versions have the same features, except for two web versions that have an additional feature. The differences between the versions are visual. In the case of the mobile application, the UI is adapted to a mobile device, which contains a smaller screen and its own platform for UI development. In the case of the web versions, the UIs have also been developed to this context, using web UI technologies. But the differences between the three web versions are changes in the navigation and UI components. In this paper, we focus on the following features of the prototype:

\begin{enumerate}

\item \textbf{Goal}: the user can check information about the general energy consumption per month. Having access to the goal and consumption in kWh for the chosen month.

\item \textbf{Filter}: the user has access to a list of all his or her objects in the house, having the possibility to filter this list per room. An object means any component that can be controlled and whose energy consumption can be registered, such as lights and electronic devices.

\item \textbf{Comparator}: the user can choose two objects and compare, side by side, their energy consumption charts. This feature is present in only two of the web versions.

\end{enumerate}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{images/web0_goal-filter.eps}
  \caption{Ajoutez une légende en dessous de chaque image.}
  \label{fig:sample}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{images/mobile_goal-filter.eps}
  \caption{Ajoutez une légende en dessous de chaque image.}
  \label{fig:sample}
\end{figure}

@@

\subsection{Discussion and Analysis}
TODO

>>>>

% =============================================================================
\section{Case Study}
% =============================================================================
TODO

@@

\subsection{Discussion and Analysis}
Firstly, the number of lines to write for tests have been at least halved, as Table \ref{table:scriptssize} shows it.
\begin{table}
\begin{tabular}{|l l|r r r r|}
\hline
test		&	implementation&	mobile	&	web0	&	web1	&	web2	\\
\hline
goal		&	plain Java	&	161		&	143		&	151		&	147		\\
			&	with Tobias	&	76		&	67		&	69		&	68		\\
\hline
filter		&	plain Java	&	/		&	350		&	402		&	369		\\
			&	with Tobias	&	/		&	88		&	93		&	92		\\
\hline
compare	&	plain Java	&	/		&	/		&	235		&	227		\\
			&	with Tobias	&	/		&	/		&	59		&	58		\\
\hline
\end{tabular}
\caption{Comparison of number of lines for various functionalities and various versions for Tobias script and its generated test}
\label{table:scriptssize}
\end{table}
Secondly, the logical structure of the various tests for a same functionality and version is shared, and so the differences between these files are very localized : in the header of the file (preferences for the test) and in the implementations of the abstract groups (version details). So there is little variation from a shared abstract script for each file, as can be seen in Table \ref{table:scripts-similarity}.
\begin{table}
\begin{tabular}{|l l|r r r|}
\hline
test		&	version&	shared	&	total	&	\%	\\
\hline
goal		&	mobile	&	48		&	76		&	63	\\
			&	web0	&	65		&	67		&	97	\\
			&	web2	&	65		&	68		&	95	\\
\hline
filter		&	web0	&	78		&	88		&	88	\\
			&	web2	&	89		&	92		&	96	\\
\hline
compare	&	web2	&	55		&	58		&	94 \\
\hline
\end{tabular}
\caption{Comparison of number of shared lines between Tobias scripts and version web1 for a same functionality}
\label{table:scripts-similarity}
\end{table}
When small changes are applied to the UI, the scripts only differ by some lines. Even in the case of a change of platform (web to mobile) the scripts stay similar.
Lastly, there is also shared lines between files, whichever their version and functionality tested, because these tests proceed by steps, which can sometimes be the same for several scripts.
So this approach allows to reduce the amount of work, while it facilitates it by reducing differences between script versions.
